---
title: "Linear and Logistic Regression Project"
author: "Meg Rosales"
date: "11/12/2019"
output: html_document
params:
 t: !r Sys.time()
---

##Preliminaries
```{r}
#current date and time
params$t
```

```{r, echo=F}
#set working directory
setwd("C:/Users/meg/Desktop/Fall 2019 Courses/Linear and Logistic Regression")

#load packages
library(dplyr)
library(psych)
library(lubridate)
library(ggplot2)
library(tidyr)
library(car)
library(ResourceSelection)
library(broom)
#load dataset
aaco <- read.csv(file = "Austin_Animal_Center_Outcomes (1).csv")
```

##Data cleaning
```{r}
#got inspiration for data cleaning only from this Kaggle notebook:
#https://www.kaggle.com/mrisdal/quick-dirty-randomforest
#see reference in project presentation/paper

#data starts at 109,915 cases

#check unique values in relevant columns
#Outcome type
unique(aaco$Outcome.Type)

#simplify analysis to only adoption or euthanasia
aaco <- aaco%>%
  filter(Outcome.Type == "Adoption"| Outcome.Type == "Euthanasia")
#55,396 observations
table(aaco$Outcome.Type)
```

```{r}
#Animal type
unique(aaco$Animal.Type)
addmargins(table(aaco$Animal.Type))

#filter to only cats and dogs
aaco <- aaco%>%
  filter(Animal.Type == "Cat"| Animal.Type == "Dog")
addmargins(table(aaco$Animal.Type))
#50,727 observations
```

```{r}
#Sex upon outcome
addmargins(table(aaco$Sex.upon.Outcome))
#unknown is missing data, so can't really infer about unknown
aaco <- aaco%>%
  filter(Sex.upon.Outcome != "NULL" & Sex.upon.Outcome !="Unknown")
addmargins(table(aaco$Sex.upon.Outcome))
#50,393 observations

#split sex upon outcome into spayed/neutered and sex
aaco$sn <- sapply(as.character(aaco$Sex.upon.Outcome),
                  function(x)
                    {unlist(strsplit(x, split = ' '))[1]})

aaco$sex <- sapply(as.character(aaco$Sex.upon.Outcome),
                  function(x)
                    {unlist(strsplit(x, split = ' '))[2]})

#generate intact binary variable
aaco$intact <- ifelse(aaco$sn == "Intact", 1, 0)

#generate female binary variable
aaco$female <- ifelse(aaco$sex == "Female", 1, 0)
          
                    
```

```{r}
#Name
#Create variable has_name
#choose all non-blank/missing cases
aaco$has_name <- ifelse(!is.na(as.character(aaco$Name))&as.character(aaco$Name)!="", 1, 0)
#addmargins(table(aaco$has_name))
```

Now on to the slightly more complicated cleaning that actually requires some decision making.

```{r}
#age
#function that takes the age upon outcome, splits it, and gets the number
tn <- function(x){
  l <- unlist(strsplit(x, split = ' '))
  return(l[1])
}

#function that takes the age upon outcome, splits it, and gets the unit
tu <- function(x){
  l <- unlist(strsplit(x, split = ' '))
  return(l[2])
}

#get numerical value of time
aaco$timenum <- as.numeric(sapply(as.character(aaco$Age.upon.Outcome), tn))

#get unit of time
aaco$timeunit <- sapply(as.character(aaco$Age.upon.Outcome), tu)
#get rid of "s" at the end for simplicity
aaco$timeunit <- gsub('s', '', aaco$timeunit)

#drop rows with missing time numbers
aaco <- aaco%>%
  drop_na(timenum)

#50,390 values

#create number of days variable
aaco$outcomeage <- aaco$timenum
#unit is days - keep same number
#change week, month, and year
#multiply by 7 for week
aaco$outcomeage[aaco$timeunit == "week"] <- 
  aaco$outcomeage[aaco$timeunit == "week"]*7
#by 30 days for month (approximate)
aaco$outcomeage[aaco$timeunit == "month"] <- 
  aaco$outcomeage[aaco$timeunit == "month"]*30
#by 365 for year
aaco$outcomeage[aaco$timeunit == "year"] <- 
  aaco$outcomeage[aaco$timeunit == "year"]*365
```

```{r}
#color
length(unique(aaco$Color))
#415 different colors

color <- aaco%>%
  group_by(Color)%>%
  summarize(count = n())%>%
  mutate(proportion = count/sum(count))%>%
  arrange(desc(proportion))
color

#add mixed color binary variable
aaco$mixedcolor <- ifelse(grepl("/",as.character(aaco$Color)), 1, 0)

#temporary variable
#take first color as primary color when there is a / present
#otherwise keep color
aaco$color2 <- ifelse(grepl('/',as.character(aaco$Color)),
                      unlist(strsplit(as.character(aaco$Color), '/'))[1],
                      as.character(aaco$Color))

#some of the colors have two words in them. take the first word
aaco$color2 <- ifelse(grepl(' ',aaco$color2),
                      unlist(strsplit(aaco$color2, ' '))[1],
                      aaco$color2)

#check colors again
color2 <- aaco%>%
  group_by(color2)%>%
  summarize(count = n())%>%
  mutate(proportion = count/sum(count))%>%
  arrange(desc(proportion))
color2

#update colors for mixed cats
aaco$mixedcolor[aaco$color2 == "Tricolor"|aaco$color2 == "Calico"|
                  aaco$color2 == "Torbie"] <-1

#consolidate browns: Sable, Chocolate
aaco$color2[aaco$color2 == "Sable"|aaco$color2 == "Chocolate"|
              aaco$color2 == "Liver"] <- "Brown"

#consolidate grays: Agouti, Silver
aaco$color2[aaco$color2 == "Agouti"|aaco$color2 == "Silver"] <- "Gray"

#consolidate tans: cream, fawn
aaco$color2[aaco$color2 == "Cream"|aaco$color2 == "Fawn"] <- "Tan"

#consolidate orange: apricot
aaco$color2[aaco$color2 == "Apricot"] <- "Orange"

#consolidate yellow: buff, gold
aaco$color2[aaco$color2 == "Buff"|aaco$color2 == "Gold"] <- "Yellow"

#multicolor cats can fall under multi
aaco$color2[aaco$color2 == "Torbie"|aaco$color2 == "Calico"|
              aaco$color2 == "Tortie"| aaco$color2 == "Tricolor"] <- "Multi"

#acceptably simplified into 10 colors for now
table(aaco$color2)

#create multinomial variable for color
#brown will be the reference category
#brown = 1, blue = 2, black = 3, gray = 4, multi = 5
#orange = 6, red = 7, tan = 8, white = 9, yellow = 10
aaco$color_num <- aaco$color2
aaco$color_num[aaco$color2 == "Brown"] <- 1
aaco$color_num[aaco$color2 == "Blue"] <- 2
aaco$color_num[aaco$color2 == "Black"] <- 3
aaco$color_num[aaco$color2 == "Gray"] <- 4
aaco$color_num[aaco$color2 == "Multi"] <- 5
aaco$color_num[aaco$color2 == "Orange"] <- 6
aaco$color_num[aaco$color2 == "Red"] <- 7
aaco$color_num[aaco$color2 == "Tan"] <- 8
aaco$color_num[aaco$color2 == "White"] <- 9
aaco$color_num[aaco$color2 == "Yellow"] <- 10
```

```{r}
#breed
length(unique(aaco$Breed))
#1723 breeds

#mixed color indicator
#mixed if says "Mix" or there's a slash present
aaco$mixedbreed <- ifelse(grepl('Mix', as.character(aaco$Breed))|
                  grepl('/', as.character(aaco$Breed)),1, 0)

#examine counts by dog and cat breed
dogbreed <- aaco%>%
  filter(Animal.Type == "Dog")%>%
  group_by(Breed)%>%
  summarize(count = n())%>%
  mutate(proportion = count/sum(count))%>%
  arrange(desc(proportion))
dogbreed

#play with cumulative proportions to see how many breeds cover all the animals
sum(head(dogbreed$proportion, n = 40))

head(dogbreed, n = 20)

# #examine graphically
# ggplot(head(dogbreed, n=20))+
#   geom_bar(aes(x = reorder(Breed, proportion), y = proportion, fill= Breed), stat = "identity")+
#   coord_flip()+
#   theme(legend.position = "none")+
#   geom_text(aes(x = reorder(Breed, proportion), y = proportion + 0.005, 
#                 label = round(proportion, 4)),
#             size = 2)+
#   xlab("Breed")

#take top 10 dog breeds
#simplify top 10 so they generalize
#Pit Bull, Retriever, Chihuahua, Shepherd, Cattle, Dachshund, Collie, Boxer,
#Terrier, Catahoula, Staffordshire, Husky, Corgi
#add huskies and corgis because I love them

#first, split any mixes
#new variable
aaco$breed2 <- aaco$Breed
#use only the first breed if split
aaco$breed2[grepl('/', as.character(aaco$breed2))] <- unlist(strsplit(as.character(aaco$breed2), '/')[1])

#new vector for the multinomialbreed variable
aaco$breed <- rep(NA, nrow(aaco))

#the 13 dog breeds will be 1 through 13
aaco$breed[grepl('Pit Bull', as.character(aaco$breed2))] <- 1
aaco$breed[grepl('Retriever', as.character(aaco$breed2))] <- 2
aaco$breed[grepl('Chihuahua', as.character(aaco$breed2))] <- 3
aaco$breed[grepl('Shepherd', as.character(aaco$breed2))] <- 4
aaco$breed[grepl('Cattle', as.character(aaco$breed2))] <- 5
aaco$breed[grepl('Dachshund', as.character(aaco$breed2))] <- 6
aaco$breed[grepl('Collie', as.character(aaco$breed2))] <- 7
aaco$breed[grepl('Boxer', as.character(aaco$breed2))] <- 8
aaco$breed[grepl('Terrier', as.character(aaco$breed2))] <- 9
aaco$breed[grepl('Catahoula', as.character(aaco$breed2))] <- 10
aaco$breed[grepl('Staffordshire', as.character(aaco$breed2))] <- 11
aaco$breed[grepl('Husky', as.character(aaco$breed2))] <- 12
aaco$breed[grepl('Corgi', as.character(aaco$breed2))] <- 13

#go on to cat breeds before simplifying all else to other
```

```{r}
#same thing for cats
catbreed <- aaco%>%
  filter(Animal.Type == "Cat")%>%
  group_by(Breed)%>%
  summarize(count = n())%>%
  mutate(proportion = count/sum(count))%>%
  arrange(desc(proportion))
catbreed

sum(head(catbreed$proportion, n = 5))
head(catbreed, n = 20)
#98% of the cats fall in the first 10 categories
#96% of the cats fall in the first 5 categories

# #examine graphically
# ggplot(head(catbreed, n= 20))+
#   geom_bar(aes(x = reorder(Breed, proportion), y = proportion, fill = Breed),
#            stat = "identity")+
#   coord_flip()+
#   geom_text(aes(x = reorder(Breed, proportion), y = proportion + 0.04, 
#                 label = round(proportion, 4)),
#             size = 3)+
#   theme(legend.position = "none")+
#   xlab("Breed")
#   

#take top 10 categories and Maine Coon (personal interest)
#several of the top are mixed, so combine mixes
#all other cats/dogs become other
aaco$breed[grepl('Domestic Shorthair', as.character(aaco$breed2))] <- 14
aaco$breed[grepl('Domestic Medium Hair', as.character(aaco$breed2))] <- 15
aaco$breed[grepl('Domestic Longhair', as.character(aaco$breed2))] <- 16
aaco$breed[grepl('Siamese', as.character(aaco$breed2))] <- 17
aaco$breed[grepl('Snowshoe', as.character(aaco$breed2))] <- 18
aaco$breed[grepl('American Shorthair', as.character(aaco$breed2))] <- 19
aaco$breed[grepl('Maine Coon', as.character(aaco$breed2))] <- 20
#other
aaco$breed[is.na(aaco$breed)] <- 21

#check breed
addmargins(table(aaco$breed))

#all breeds accounted for
```

```{r}
#date/time of outcome
#assuming this is date/time of outcome - hopefully the records are correct

#attempted to clean the data with this idea, but it didn't work
#we have plenty of other variables and data to look at, so I'll just examine the other variables for now


# #check day, month, year, and hour
# aaco$hour <- hour(as.character(aaco$DateTime))
# aaco$day <- day(as.character(aaco$DateTime))
# aaco$month <- month(aaco$DateTime)
# aaco$year <- year(aaco$DateTime)
```


```{r}
#create final dataset and save so we don't have to keep cleaning every time
final <- aaco%>%
  select(c(Outcome.Type, Animal.Type, has_name, outcomeage, intact, female, mixedcolor,color_num, mixedbreed, breed))

#make outcome variable 1-0 binary for adopted (1 = yes, 0 = no)
final$outcome <- ifelse(final$Outcome.Type == "Adoption", 1, 0)

#make animal type variable 1-0 for cat (1 = yes, 0 = no (dog))
final$cat <- ifelse(final$Animal.Type == "Cat", 1, 0)

#drop Outcome.Type and Animal.Type variables
final <- final%>%
  select(-c(Outcome.Type, Animal.Type))

#save the data in an Rdata file
save(final, file = "fullanimaldata24Nov19.Rdata")
```

##Analysis

```{r}
#load the Rdata file
load("fullanimaldata24Nov19.Rdata")

#look at dataset structure
str(final)

#everything is numeric right now, but the only continuous variable is outcome age
```

###Variable Selection

```{r}
#check individual logistic regressions for significance

#change color number to a factor
final$color_num <- as.factor(as.numeric(final$color_num))

#breed is also a factor
final$breed <- as.factor(final$breed)

#binary variables are already coded, so should give the same results regardless
#of whether they're factors or not

#change variable order for convenience
final <- final[c("cat", "has_name", "outcomeage", "intact", "female", "mixedcolor", "color_num", "mixedbreed", "breed", "outcome")]

#check all variables for significance except outcome
#doing it this way so I can check the significance for each different factor of the breed and color variables
i = 1
for(var in final[1:9]){
  print(colnames(final)[i])
  model <- glm(outcome ~ var, final,
               family = binomial(link = "logit"))
  print(summary(model))
  i = i + 1
}

#going to run into the large sample problem here since n = 50,390
```

Here, we are running into the large sample problem for significance. I'll look at cats and dogs separately first to see if we can identify any trends.

```{r}
#cat data
cat <- final%>%
  filter(cat == 1)

#outcome variable table
table(cat$outcome)

#need to recode breed because we only have cat breeds, so the reference
#category no longer holds
table(cat$breed)
cat$breed <- as.factor(as.numeric(cat$breed) - 13)

#look at cat colors - we don't have any for color #7, but that's okay
#because it's a factor
table(cat$color_num)

#change to factor variable
cat$color_num <- as.factor(cat$color_num)

#univariable logistic regression for cat
i = 1
for(var in cat[1:9]){
  print(colnames(cat)[i])
  model <- glm(outcome ~ var, cat,
               family = binomial(link = "logit"))
  print(summary(model))
  i = i + 1
}

#colors: only color 3 is non-significant at p < 0.25
#breed: Breeds 2, 4, 7, and 8 are non-significant at p < 0.25. Breed 5 is close at p = 0.27


```

##Attempt 1: original coding of breed and color
#Model 1: All variables present
```{r}
#add all the variables into the main model
cat1 <- glm(outcome ~ has_name + outcomeage + intact + female + mixedcolor +
              color_num + mixedbreed + breed, cat,
            family = binomial(link = "logit"))
summary(cat1)
#get odds ratios and confidence intervals
cbind(exp(coef(cat1)), exp(confint(cat1)))

#based on significance at p <0.05, eliminate mixed color
#should reconsider how breed and color are coded based on these and
#above results

#for now, continue with the process
cat2 <- glm(outcome ~ has_name + outcomeage + intact + female +
              color_num + mixedbreed + breed, cat,
            family = binomial(link = "logit"))
summary(cat2)
cbind(exp(coef(cat2)), exp(confint(cat2)))

#likelihood ratio test for new model
anova(cat1, cat2, test = "LRT")

#non-significant, new model doesn't fit better

#the model just looks super cumbersome with all those breeds and colors
#need to simplify further and try again
```

```{r}
#look at cat colors
table(cat$color_num)

#from the univariable logistic regression
#3, 4, 5, 6, and 9 were significant  (black, gray, multi, orange, white)
#instead of color num variable, I'll recode into binary for black, orange, white,
#and brown

cat$black <- ifelse(cat$color_num == "3", 1, 0)
cat$orange <- ifelse(cat$color_num == "6", 1, 0)
cat$brown <- ifelse(cat$color_num == "1", 1, 0)
cat$white <- ifelse(cat$color_num == "9", 1, 0)
cat$gray <- ifelse(cat$color_num == "4", 1, 0)
cat$multi <- ifelse(cat$color_num == "5", 1, 0)

#look at cat breeds
table(cat$breed)

#From univariable logistic regression above: Breeds 2, 4, 7, and 8 are #non-significant at p < 0.25. Breed 5 is close at p = 0.27

#create binary variables for all the rest of the breeds
cat$domsh <- ifelse(cat$breed == "1", 1, 0)
cat$domlong <- ifelse(cat$breed == "3", 1, 0)
cat$snowshoe <- ifelse(cat$breed == "5", 1, 0)
cat$amsh <- ifelse(cat$breed == "6", 1, 0)

#get rid of the old breed and color variables
#and cat because we know these are all cats
cat <- cat%>%
  select(-c(cat, color_num, breed))

#changed name for outcome variable and then added it to the end to make
#data easier to work with
cat$adopted <- cat$outcome

#drop old outcome variable
cat <- cat%>%
  select(-c(outcome))

#actually going to save my data this time
save(cat, file = "catdata24Nov19.Rdata")
```

At this point, I decided to simplify the project and only analyze the cat
data.

##Attempt 2: New and improved color and breed variables

#Univariable logistic regressions
```{r}
i = 1
for(var in cat[1:16]){
  print(colnames(cat)[i])
  model <- glm(adopted ~ var, cat,
               family = binomial(link = "logit"))
  print(summary(model))
  i = i + 1
}

```

Only black and brown were non-significant at this point. Add all other variables to the full model.

**Step 1: Full model**
```{r}
cat_full <- glm(adopted ~ has_name + outcomeage + intact + female + mixedcolor +
                  mixedbreed + orange + white + gray + multi + domsh + domlong +
                  snowshoe + amsh, data = cat,
                family = binomial(link = "logit"))
summary(cat_full)

#non-significant variables: mixedcolor, white, gray, multi, domlong, snowsh, amsh

#reduced model
cat_reduced <- glm(adopted ~ has_name + outcomeage + intact + female + mixedbreed + orange + domsh, data = cat,
                   family = binomial(link = "logit"))
summary(cat_reduced)

#compare to full model
anova(cat_reduced, cat_full, test = "Chisq")

#non-significant, reduced model is better
#however, the coefficient for domestic shorthair changed by 0.2058465
#so fit another model adding back mixedcolor since that was the closest to
#nonsignificant last time

cat_reduced2 <- glm(adopted ~ has_name + outcomeage + intact + female + mixedcolor + mixedbreed + orange + domsh, data = cat,
                   family = binomial(link = "logit"))
summary(cat_reduced2)

#compared to the full model, domsh is only reduced by 16%, which is less than 20%
#all others are reduced by less that 20% 
#visually inspected and calculated change for suspicious variables with calculator

#compare new reduced model to the full model
anova(cat_full, cat_reduced2, test = "Chisq")

#non-significant, so reduced model fits better
```

#Adding back variables omitted after Step 1 in case they matter in terms of the other variables
```{r}

#only black and brown were omitted in Step 1 - all other variables were removed
#in Step 2

#black
summary(glm(adopted ~ black + has_name + outcomeage + intact + female + mixedcolor + mixedbreed + orange + domsh, data = cat,
                   family = binomial(link = "logit")))

#brown
summary(glm(adopted ~ brown + has_name + outcomeage + intact + female + mixedcolor + mixedbreed + orange + domsh, data = cat,
                   family = binomial(link = "logit")))

#both black and brown are significant after being added back
#add both back to the model
cat_step3 <- glm(adopted ~ black + brown + has_name + outcomeage + intact + female + mixedcolor + mixedbreed + orange + domsh, data = cat,
                   family = binomial(link = "logit"))
summary(cat_step3)

#black remains significant, but brown is not, so only add back black

#preliminary main effects model with ORs and confidence intervals to see if
#they make sense
cat_prelim <- glm(adopted ~ black + has_name + outcomeage + intact + female + mixedcolor + mixedbreed + orange + domsh, data = cat,
                   family = binomial(link = "logit"))
summary(cat_prelim)
cbind(exp(coef(cat_prelim)),exp(confint(cat_prelim)))

#but neither domestic shorthair nor mixedcolor are significant when black is
#added back in. remove these two variables
cat_prelim2 <- glm(adopted ~ black + has_name + outcomeage + intact + female + mixedbreed + orange, data = cat,
                   family = binomial(link = "logit"))
summary(cat_prelim2)
cbind(exp(coef(cat_prelim2)),exp(confint(cat_prelim2)))

#compare fit to larger model
anova(cat_prelim, cat_prelim2, test = "Chisq")

#This is our main effects model

#now check linearity of outcomeage with logit
cat_lo <- loess(adopted~outcomeage, data = cat)
#get probabilities
logit_cat <- logit(predict(cat_lo))
#linear model of probabilities vs. outcomeage
cat_lm <- lm(logit_cat~ cat$outcomeage)

#plot probabilities vs. outcomeage
plot(cat$outcomeage, logit_cat)
abline(cat_lm)
title("Plot of Logit vs. Loess")

#that doesn't look very linear. We see a sharp rise and fall in the early days,
#a rounded drop, and then a sharper decline around about 5750 days

#create some categories

#logit peaks around a fifth of outcome age
#would make sense if that's about a year, or 365 days
#make 1 year old kittens the reference category
#cat$age1 <- ifelse(cat$outcomeage <=365, 1, 0)

#second point looks to be not quite to 1000 days
#logical point might be 2.5 years, or 913 days
cat$age1 <- ifelse(cat$outcomeage >365 & cat$outcomeage <= 913, 1,0)
#a little curvy but near linear to around 5900 days
cat$age2 <- ifelse(cat$outcomeage > 913 & cat$outcomeage <= 5900, 1, 0)
#very senior cats
cat$age3 <- ifelse(cat$outcomeage > 5900, 1, 0)

#check if categories are individually related to outcome when added in
cat_age1 <- glm(adopted ~ black + has_name + intact + female + mixedbreed + orange + age1, data = cat,
                   family = binomial(link = "logit"))
summary(cat_age1)

cat_age2 <- glm(adopted ~ black + has_name + intact + female + mixedbreed + orange + age2, data = cat,
                   family = binomial(link = "logit"))
summary(cat_age2)

cat_age3 <- glm(adopted ~ black + has_name + intact + female + mixedbreed + orange + age3, data = cat,
                   family = binomial(link = "logit"))
summary(cat_age3)

#all were significant individually

#add all categories to the model
cat_main <- glm(adopted ~ black + has_name + intact + female + mixedbreed + orange + age1 + age2 + age3, data = cat,family = "binomial"(link = "logit"))
summary(cat_main)
                   
#all three categories were significant, but the odds ratios were quite
#different, so this parametrization seems helpful. When age categories are taken
#into account, orange is no longer significant, so try again
cat_main2 <- glm(adopted ~ black + has_name + intact + female + mixedbreed +  age1 + age2 + age3, data = cat,
                   family = binomial(link = "logit"))
summary(cat_main2)
cbind(exp(coef(cat_main2)),exp(confint(cat_main2)))

#compare model with and without orange
anova(cat_main, cat_main2, test = "Chisq")

#just barely non-significant, so the model without orange is a slightly better fit

#this is our solidified main effects model
```

#Interactions
```{r}
#see if any interactions are significant`
names <- c("black", "has_name", "intact","female","mixedbreed", "age1", "age2", "age3")

#initalize lists for names, coefficients, and p-values
nia <- NULL
coia <- NULL
pia <- NULL

#example to check format
ia <- glm(formula = adopted ~ black + has_name + intact + female + mixedbreed + age1 + age2 + age3 + black:intact,
    family = binomial(link = "logit"), data = cat)
summary(ia)
#values are on the 10th row of the coefficients

#initialize list indices
k = 1

#interaction models
for(i in 1:length(names)){
  j = i+1
  while(j <= length(names)){
    var1 <- names[i]
    var2 <- names[j]
    call<-paste("glm(adopted~black+has_name+intact+female+mixedbreed+age1+age2+age3+",
                var1,":",var2,
                ",data=cat,family=binomial(link=logit))",sep="")
    ig <- eval(parse(text = call))
    igs <- summary(ig)
    if(!(var1%in%c("age1", "age2","age3") & (var2%in%c("age1", "age2","age3")))){
      nia[k] <- paste(var1, ":", var2)
      coia[k] <- coef(igs)[10,1]
     pia[k] <- coef(igs)[10,4]
    }
    
    # nia[k] <- paste(var1, ":", var2)
    # coia[k] <- coef(igs)[10,1]
    # pia[k] <- coef(igs)[10,4]
    
    j = j + 1
    k = k + 1
  }
}

ia_data <- as.data.frame(cbind(nia, coia, pia))
ia_data

#list of significant interactions
#has_name:intact, has_name:mixedbreed, has_name:age2, intact:mixedbreed, intact:age1, intact:age2, mixedbreed:age2
```


```{r}
#add interactions to the model
interactions <- glm(formula = adopted ~ black + has_name + intact + female + mixedbreed + age1 + age2 + age3 + black:mixedbreed + has_name:intact + has_name:mixedbreed + has_name:age2 + intact:mixedbreed + intact:age1 + intact:age2,
    family = binomial(link = "logit"), data = cat)
summary(interactions)

#can drop black:mixedbreed, intact:mixedbreed, intact:age1, intact:age2

#drop non-significant interactions
interactions2 <- glm(formula = adopted ~ black + has_name + intact + female + mixedbreed + age1 + age2 + age3 + has_name:intact + has_name:mixedbreed + has_name:age2,
    family = binomial(link = "logit"), data = cat)
summary(interactions2)
#ORs and confidence intervals
cbind(exp(coef(interactions2)),exp(confint(interactions2)))
```

```{r}
#intact:mixedbreed was closest to significant, so add it back
interactions3 <- glm(formula = adopted ~ black + has_name + intact + female + mixedbreed + age1 + age2 + age3 + has_name:intact + has_name:mixedbreed + has_name:age2 + intact:mixedbreed,
    family = binomial(link = "logit"), data = cat)
summary(interactions3)

#See if this model fits better
anova(interactions2, interactions3, test = "Chisq")

#Fits better with intact:mixed breed added
#Does it fit better than the full interaction model?
anova(interactions, interactions3, test = "Chisq")

#Yes. Finally, the final model
#get odds ratios and confidence intervals
cbind(exp(coef(interactions3)),exp(confint(interactions3)))
```


##Model goodness of fit
```{r}
#Check goodness of fit with Hosmer-Lemeshow Goodness of Fit test
hoslem.test(cat$adopted, fitted(interactions3), g = 10)

#fit is quite poor...revisit this after diagnostics
```

##Assumptions

```{r}

#Outcome is binary: adopted = 1, not adopted/euthanized = 0

#Already checked for linearity of outcomeage with the logit of adopted. All other predictor variables are #categorical. 

#Check for multicollinearity within the main model - obviously there will be a relationship between
#the variables with interaction terms, so use main model
vif(cat_main2)

#Nothing over 5, so we're good

#Check for influential values in continuous variable outcomeage
#anything with a Cook's distance larger than 4/n is suspect
#add Cook's distance to dataframe
cat$cooks <- cooks.distance(interactions3)

#look at the outliers
high_lev <- cat%>%
  filter(cooks > 4/nrow(cat))
high_lev

#624 rows - yikes. Let's try getting rid of the outliers?
no_ol <- cat%>%
  filter(cooks < 4/nrow(cat))

#try final model again without outliers
final_no_ol <- glm(formula = adopted ~ black + has_name + intact + female + mixedbreed + age1 + age2 + age3 + has_name:intact + has_name:mixedbreed + has_name:age2 + intact:mixedbreed,
    family = binomial(link = "logit"), data = no_ol)
summary(final_no_ol)

#this fails because getting rid of the outliers seems to have introduced complete separation
#somewhere in the model

#ORs and confidence intervals
cbind(exp(coef(final_no_ol)),exp(confint(final_no_ol)))

#goodness of fit - would have done this if getting rid of the outliers had worked
#hoslem.test(cat$adopted, fitted(final_no_ol), g = 10)
```

